Exploratory Analysis Reece C

### 2025-12-08 Exploratory Analysis Reece C.Rmd
Exploratory graphs & clustering
why are these files untracked?

cluster_data = merged %>%
  select(where(is.numeric)) %>%
  drop_na()

@@

long_df = full_merge %>%
  pivot_longer(cols = c("mean_Temp", "mean_pH", "mean_Conductivity", "mean_Turbidity",
                        "alkalinity", "hardness", "Ferric.chloride..mg.L", "Cationic.Polimer..mg.L"),
               names_to = "metric",
               values_to = "value")

>>>>

```{r}
cluster_data = merged %>%
  select(where(is.numeric)) %>%
  drop_na()

@@

names(full_merge) = c("Temperature", "pH", "Conductivity", "Turbidity", "Date", "Alkalinity",
                      "Hardness", "Cluster", "Ferric Chloride, mg/L", "Cationic Polimer, mg/L")

long_df = full_merge %>%
  pivot_longer(cols = c("Temperature", "pH", "Conductivity", "Turbidity",
                      "Alkalinity", "Hardness", "Ferric Chloride, mg/L", "Cationic Polimer, mg/L"),
               names_to = "metric",
               values_to = "value")
